The Role of Context in Spatial Region Identification

### 2013-11-10 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
jk fixed more typos

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
\begin{tabular}{c c c} 
  \begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
%  \caption{\textit{The front of the classroom} could be defined as the area between the desks and the whiteboard where people give presentations.}
  \caption{\textit{The front of the classroom}.}
  \end{subfigure} &
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
%  \caption{\textit{Safety for the scout} is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
  \caption{\textit{The safe region for the scout}.}
\end{subfigure} & 
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
%  \caption{A \textit{bottleneck} occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
 \caption{\textit{The bottleneck}.}
  \label{fig:safety}
  \end{subfigure}\\
\end{tabular}
  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

@@

We developed two experimental tasks that each address both research questions:
\begin{itemize}
	\item{Task 1:} Subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimulus that defined the CDSR (or stating there was no such region).
	\item{Task 2:} Subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well the location fit with their understanding of the CDSR on a five point Likert scale.
\end{itemize}

We developed a set of visual stimuli depicting different contexts, and paired each with an accompanying linguistic description of a CDSR (see Figure \ref{fig:exp_stimuli}). These stimuli were used in both Task 1 and 2. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the situation: (1) the classroom stimuli were always accompanied by the spatial description \emph{the front of the classroom}; (2) the military engagement stimuli were always accompanied by the description \emph{safety}; and (3) the geographical map stimuli were always accompanied by the description \emph{the bottleneck}.

@@

We use \textbf{Cohen's kappa coefficient}, $\kappa$, to measure the agreement between two regions as follows.  We generated a set of 47,000 test points that were uniformly distributed across each stimulus and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject, we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimulus basis. In this calculation, if either of the subjects in a pair entered a no region response for a particular stimulus a $\kappa$ value of 0 was used.  $\kappa$ ranges from 0 indicating no agreement to 1 indicating complete agreement.  Typically, scores above 0.4 are considered fair agreement and 0.75 considered excellent.

@@

\begin{table}[t]
\parbox{.50\linewidth}{
\centering 
\begin{tabular}{l c c}
% Stim ID & Average Pairwise $\kappa$ & No Region Responses\\
 & Average & No \\
Stim ID & Pairwise $\kappa$ & Reg.\\
\hline
\hline
(h) & 0.5034 & 0\\ % 1_2
(g) & 0.4585 & 1\\ % 1_1
(k) & 0.4548 & 0\\ % 3_3
(f) & 0.3930 & 0\\ % 2_4
(i) & 0.3906 & 0\\ % 3_1
(e-flipped) & 0.3813 & 2\\ % 2_3
(j) & 0.3787 & 1\\ % 3_2
(f-flipped) & 0.3720 & 2\\ % 2_5
(e) & 0.3629 & 1\\ %2_2
(l) & 0.3164& 0\\ % 3_4
(c) & 0.2438 & 2\\ % 2_6
(c-flipped) & 0.2414 & 4\\ %2_7
(a) & 0.0996 & 10 \\ % 2_1
\hline
\end{tabular}
\caption{The average pairwise $\kappa$ scores and the number of no region response by visual stimulus.}
\label{tab:stimuli-kappa-scores}
}
\hfill
\parbox{.50\linewidth}{
\centering
\begin{tabular}{c c}
Expected Relationship & Human Results  \\
\hline
\hline
area(g) > area(h) & 291.2 > 276.2\footnotemark[2] \\
maxX(f) > maxX(e) & 176.1 > 167.1 \\
% minimumX(e-flipped) > minimumX(f-flipped) & 336.1 > 321.3 (p<.12) \\
minX(e-flipped)  &  \\
 > minX(f-flipped) & 336.1 > 321.3\footnotemark[2] \\
maxY(i) > maxY(j) & 304.64 > 265.04\footnotemark[2] \\
maxY(j) > maxY(k) & 265.04 > 251.71 \\
maxY(k) = maxY(l) & 265.04 != 290.03 \\
\hline
\end{tabular}
\caption{Comparison of the expected relationships to the mean human responses.}
\label{tab:region-location-tests}
}
\end{table}

\footnotetext[2]{Significance value from t-test (p<0.1)}

@@

Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimulus used in the experiment and the number of no region responses for each stimulus.  It is clear from this table that the less common stimuli have the lowest $\kappa$ scores.  Each of the non-typical regions, the turret +1 arrangement (l), the u-shaped layouts (c and c-flipped), and the circle layout have kappa scores of less than 0.35. Looking at the classroom results as a whole supports the hypothesis that the definition of CDSRs in a given context is affected by the location and orientation of objects in the environment.  This dependence is observed by the fact that just moving the desks into a circle configuration the shared understanding of the front of the room no longer exists.

@@

%The analysis of the task 1 trials indicates that, over a range of domains and spatial regions, the responses from the subjects did agree, to a good degree. Furthermore, their results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment. For example, focusing on the classroom scenes (stimuli, $a$, $c$, $e$, and $f$) the only difference between these trials was the layout of the chairs in the room and yet there is a substantial variation across these stimuli of the agreement between subjects on the specified spatial region, namely \textit{the front of the room}. Situation $f$ resulted in an average pairwise agreement of $0.393$ and in comparision context $a$ had an average pairwise agreement of $0.0996$.

@@

\subsection{Task 2 - Design} 
In task two, a location was marked on the stimulus (using a red dot) and the subject was asked to rank on a five point Likert scale how well the location matched the given CDSR, or select not applicable.  The location of these points was informed by the results of a pilot study, such that one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the CDSR. In the classroom domain, the three points were located along the horizontal line that bisected the stimulus with P1 positioned on the left of the stimulus, P2 in the center and P3 on the right of the stimulus. This provides comparable data points between the trials where the classroom stimuli were horizontally flipped.  In the geography situations, P1 was positioned in the top left corner of the stimulus, P2 was the expected sweetspot and was located within the expected bottleneck region for both stimulus and P3 was located in the bottom right corner of the stimulus.  In the military engagement domain the three test points were located on the vertical line that bisected the stimulus: P1 was located near the enemy tanks, P3 was located with all friendly units between it and the enemy tanks and P2 was located near the center of the image as follows. In stimuli (j) and (k) the point lay between all forces, in stimulus (i), it lay behind the friendly tanks, and in stimulus (l) , it lay behind the lone turret but in front of the row turrets.  P3 was the expected sweetspot in the military engagement domain but the rating of P2 should differ with (i) receiving the highest score and (k) the lowest score.

@@

%Task 1: The participant draws a polygon denoting the region
%Analysis of results:
%(1) Do participants agree/understand-the-task? (validation of approach) + Should anyone be excluded?
%Within the data for each trial,
%-- For each participant, generate the intersection and union polygon of all the other participants
%---- Generate N random points in the area of the full stimulus
%---- For each of these N points check whether the participant's polygon and the [intersection/union] polygon both include it (agree++) or if one includes it and the other doesn't (disagree++)
%---- Then we calculate a Cohen Kappa score as a measure of agreement between the participant and eveyone else. Note we need to calculate the chance of random agreement but we can do this as a function over the relative size of the participant's polygon in the total area of the stimulus and the relative size of the intersection/union polygon
%(see http://en.wikipedia.org/wiki/Cohen%27s_kappa )
%This process will result in for each trial a list of kappa scores for each participant indicating the extent to which they agree with everyone else. We are hoping for a high kappa score
%(2) Does context matter?
%I understand that all the rooms stimuli have the same extent.
%So one way of evaluating whether context matters is to use the kapp score between the intersection/union polygon generated using all the response (less the excluded partitipants) for one trial and the equivalent polygon for another trial.
%We are hoping for a low kappa score

%Cohen's kappa measures the agreement between two annotators who each classify a number of items into two or more mutually exclusive classes as is defined as follows:
%\begin{equation*}
%\kappa = \frac{P(a)-P(ca)}{1-P(ca)}
%\end{equation*}
%where $P(a)$ is the observed relative agreement between the annotators, and $P(ca)$ is the probability of a chance agreement between these to annotators.

@@

%The type 2 trials the same visual stimulus and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on %the visual stimulus (using a red dot) and the subject was asked to rank on a five point Likert scale their judgement of how well the location matched %the described spatial region. For each stimulus domain (classroom, map, military engagement) three points (P1, P2, and P3) were pre-selected.

Table \ref{tab:point-likert-scores} lists the average Likert scores for the different points in each context. In all contexts, the expected sweetspot received the maximum average Likert rating that was statistically significant using one-tailed two-sample t-tests $(p<.05)$.  To control for left--right bias, we compared the ratings of sweetspots in the classroom stimuli (c), (e), and (f) with their flipped variants.  There was no statistical difference between the stimuli and their flipped variants.  These Likert ratings on individual stimuli support the claim that people are able to agree on the locations of CDSRs with changing context.

%There were two of these t-tests carried out for each stimulus, each one tested whether the sweetspot ranking was statistically higher than one of the other points. Table \ref{tab:point-likert-scores} also lists the results of these t-tests for each stimulus. In all cases, the results indicate that the null hypothesis, $H_0$, should be rejected and that the alternative hypothesis, namely that the sweetspot was rated significantly higher than the other point, could be accepted with $\alpha=0.05$.

%As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two-sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli using a confidence level of $95\%$. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli. %lending support for question 2 ...

@@

Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the military domain between the stimuli (i) and (j) and the stimuli (k) and (l). In stimulus (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimulus (j) the P2 point is in no-man's land. Given this change in context one would expect a higher ranking for the P2 point in context (i) than in context (j). This is confirmed by the results in Table \ref{tab:point-likert-scores} and the higher rating is statistically significant $(p<.05)$. Stimuli (k) and (l) present an analagous context with P2 being protected by an extra turret in stimulus (l) but in no-man's land in stimulus (k). Again, the average rating of P2 for stimulus (l) is higher than that of (k), although this difference is not statistically significant. Thus, it is unclear the extent to which participants were simulating the outcome of the battle. Notice, that the rating of the sweetspot for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different sweetspots across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.

@@

Taken together these results indicate that: (1) for all stimuli there was a location that was considered to be inside the region described by the linguistic term and that other locations were considered to be outside of this region; (2) within each domain the particular location that was considered to be the sweetspot was determined by the particular context depicted in the visual stimulus (i.e., changes in the position and orientation of objects with functional significance effected the location of the region); and (3) the impact of the changes in the depicted context was consistent across similar contexts, as shown by the fact that the sweetspot flipped from P1 to P3 when the context was flipped.

%-----------------
%
%Task 2: The participant selected a point denoting the sweetspot of the region
%Analysis of results:
%(1) Do participants agree/understand-the-task? (validation of approach) + Should anyone be excluded?
%Compare the variance across the subjects with the variance across a number of set of randomly generate points, where set size equals the number of participants, using the F distribution (http://www.ltcconline.net/greenl/courses/201/regression/comparingVariances.htm) where we are checking if the variance of the random points are greater than that of the participants.
%We would hope that the variance of the subjects responses is lower than that of randomly generated points.
%After the initial comparison with the random point sets we may exclude participants based on extreme variance.
% 
%(2) Does context matter?
%Do the clusters of participants responses move?
%- for each experimental stimulus compute the mean x and y location for the responses for that trial
%- check whether the variance between the means of different stimuli responses is greater than the variance within each stimulus responses.

%-----------------
%
%
%Task 3: The participant grades a point with respect to membership of the region on a Likert scale
%I understand this experiment to be useful because (a) it asks the participants to evaluate (rather than generate cf task 1 and 2) (b) hopefully we can use it to reinforce our findings in task 1 and task 2
%I think we need to be careful that the points we present to people for evaluation are reasonably well distributed so that we have a good chance of getting a variation across the responses
%Assuming that there is a variation across the Likert scores for a particular stimulus then check if their is a correlation between the scores and:
%(a) inclusion in the intersection/union polygons from task 1 for the same stimulus
%(b) distance from the mean sweet spot for that stimulus from task 2
%
%-----------------

@@

%Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.
%
%However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all the way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.
%
%The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

>>>>

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
\begin{tabular}{c c c} 
  \begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
%  \caption{``The front of the classroom'' could be defined as the area between the desks and the whiteboard where people give presentations.}
  \caption{``The front of the classroom''.}
  \end{subfigure} &
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
%  \caption{Safety for the scout is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
  \caption{``The safe region for the scout''.}
\end{subfigure} & 
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
%  \caption{A bottleneck occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
 \caption{``The bottleneck''.}
  \label{fig:safety}
  \end{subfigure}\\
\end{tabular}
  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

@@

We developed two experimental tasks that each address both research questions:
\begin{itemize}
	\item{Task 1:} Subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimulus that defined the CDSR (or stating there was no such region).
	\item{Task 2:} Subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well the location fit with their understanding of the CDSR on a five point \textit{Likert scale}.
\end{itemize}

We developed a set of visual stimuli depicting different contexts, and paired each with an accompanying linguistic description of a CDSR (see Figure \ref{fig:exp_stimuli}). These stimuli were used in both Task 1 and 2. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the situation: (1) the classroom stimuli were always accompanied by the spatial description ``the front of the classroom''; (2) the military engagement stimuli were always accompanied by the description ``safety''; and (3) the geographical map stimuli were always accompanied by the description ``the bottleneck''.

@@

We use \textit{Cohen's kappa} coefficient, $\kappa$, to measure the agreement between two regions as follows.  We generated a set of 47,000 test points that were uniformly distributed across each stimulus and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject, we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimulus basis. In this calculation, if either of the subjects in a pair entered a no region response for a particular stimulus a $\kappa$ value of 0 was used.  $\kappa$ ranges from 0 indicating no agreement to 1 indicating complete agreement.  Typically, scores above 0.4 are considered fair agreement and 0.75 considered excellent.

@@

%\begin{table}[t]
%\parbox{.50\linewidth}{
%\centering 
%\begin{tabular}{l c c}
%% Stim ID & Average Pairwise $\kappa$ & No Region Responses\\
% & Average & No \\
%Stim ID & Pairwise $\kappa$ & Reg.\\
%\hline
%\hline
%(h) & 0.5034 & 0\\ % 1_2
%(g) & 0.4585 & 1\\ % 1_1
%(k) & 0.4548 & 0\\ % 3_3
%(f) & 0.3930 & 0\\ % 2_4
%(i) & 0.3906 & 0\\ % 3_1
%(e-flipped) & 0.3813 & 2\\ % 2_3
%(j) & 0.3787 & 1\\ % 3_2
%(f-flipped) & 0.3720 & 2\\ % 2_5
%(e) & 0.3629 & 1\\ %2_2
%(l) & 0.3164& 0\\ % 3_4
%(c) & 0.2438 & 2\\ % 2_6
%(c-flipped) & 0.2414 & 4\\ %2_7
%(a) & 0.0996 & 10 \\ % 2_1
%\hline
%\end{tabular}
%\caption{The average pairwise $\kappa$ scores and the number of no region response by visual stimulus.}
%\label{tab:stimuli-kappa-scores}
%}
%\hfill
%\parbox{.50\linewidth}{
%\centering
%\begin{tabular}{c c}
%Expected Relationship & Human Results  \\
%\hline
%\hline
%area(g) > area(h) & 291.2 > 276.2\footnotemark[2] \\
%maxX(f) > maxX(e) & 176.1 > 167.1 \\
%% minimumX(e-flipped) > minimumX(f-flipped) & 336.1 > 321.3 (p<.12) \\
%minX(e-flipped)  &  \\
% > minX(f-flipped) & 336.1 > 321.3\footnotemark[2] \\
%maxY(i) > maxY(j) & 304.64 > 265.04\footnotemark[2] \\
%maxY(j) > maxY(k) & 265.04 > 251.71 \\
%maxY(k) = maxY(l) & 265.04 != 290.03 \\
%\hline
%\end{tabular}
%\caption{Comparison of the expected relationships to the mean human responses.}
%\label{tab:region-location-tests}
%}
%\end{table}
%\footnotetext[2]{Significance value from t-test (p<0.1)}

\begin{table}[htb]
\begin{center}
\begin{tabular}{l c c}
% Stim ID & Average Pairwise $\kappa$ & No Region Responses\\
Stim ID & Average Pairwise $\kappa$ & No Reg.\\
\hline
\hline
(h) & 0.5034 & 0\\ % 1_2
(g) & 0.4585 & 1\\ % 1_1
(k) & 0.4548 & 0\\ % 3_3
(f) & 0.3930 & 0\\ % 2_4
(i) & 0.3906 & 0\\ % 3_1
(e-flipped) & 0.3813 & 2\\ % 2_3
(j) & 0.3787 & 1\\ % 3_2
(f-flipped) & 0.3720 & 2\\ % 2_5
(e) & 0.3629 & 1\\ %2_2
(l) & 0.3164& 0\\ % 3_4
(c) & 0.2438 & 2\\ % 2_6
(c-flipped) & 0.2414 & 4\\ %2_7
(a) & 0.0996 & 10 \\ % 2_1
\hline
\end{tabular}
\end{center}
\caption{The average pairwise $\kappa$ scores and the number of no region response by visual stimulus.}
\label{tab:stimuli-kappa-scores}
\end{table}

\begin{table}[htb]
\begin{center}
\begin{tabular}{r c l r c l}
\multicolumn{3}{c}{Expected Relationship} & \multicolumn{3}{c}{Human Results}  \\
\hline
\hline
area(g) &>& area(h) & 291.2 & >& 276.2* \\
maxX(f) &>& maxX(e) & 176.1& >& 167.1 \\
% minimumX(e-flipped) &>& minimumX(f-flipped) & 336.1& >& 321.3 (p<.12) \\
minX(e-flipped) &>& minX(f-flipped) & 336.1& >& 321.3* \\
maxY(i) &>& maxY(j) & 304.64 &>& 265.04* \\
maxY(j) &>& maxY(k) & 265.04 &>& 251.71 \\
maxY(k) &=& maxY(l) & 265.04 &!=& 290.03 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the expected relationships to the mean human responses. *Significance value from t-test (p<0.1).}
\label{tab:region-location-tests}
\end{table}

@@

Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimulus used in the experiment and the number of no region responses for each stimulus.  It is clear from this table that the less common stimuli have the lowest $\kappa$ scores.  Each of the non-typical regions, the turret +1 arrangement (l), the u-shaped layouts (c and c-flipped), and the circle layout have kappa scores of less than 0.35. Looking at the classroom results as a whole supports the hypothesis that the definition of CDSRs in a given context is affected by the location and orientation of objects in the environment. An extreme example of this relationship between the configuration of objects in a context and the meaning of a CDSR is that our results indicate that the shared understanding of ``the front of the room'' breaks down in the classroom setting when the chairs in the room are moved into a circle configuration as indicated by the fact that context (a) (Figure \ref{fig:classroom-a}) had an extremly low average pairwise agreement of  $0.0996$).

@@

%The analysis of the task 1 trials indicates that, over a range of domains and spatial regions, the responses from the subjects did agree, to a good degree. Furthermore, their results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment. For example, focusing on the classroom scenes (stimuli, $a$, $c$, $e$, and $f$) the only difference between these trials was the layout of the chairs in the room and yet there is a substantial variation across these stimuli of the agreement between subjects on the specified spatial region, namely ``the front of the room''. Situation $f$ resulted in an average pairwise agreement of $0.393$ and in comparision context $a$ had an average pairwise agreement of $0.0996$.

@@

\subsection{Task 2 - Design} 
In task two, a location was marked on the stimulus (using a red dot) and the subject was asked to rank on a five point \textit{Likert scale} how well the location matched the given CDSR, or select not applicable.  The location of these points was informed by the results of a pilot study, such that one of the domain's points, called the \textit{sweetspot}, was located near the expected prototypical center of the CDSR. In the classroom domain, the three points were located along the horizontal line that bisected the stimulus with P1 positioned on the left of the stimulus, P2 in the center and P3 on the right of the stimulus. This provides comparable data points between the trials where the classroom stimuli were horizontally flipped.  In the geography situations, P1 was positioned in the top left corner of the stimulus, P2 was the expected \textit{sweetspot} and was located within the expected bottleneck region for both stimulus and P3 was located in the bottom right corner of the stimulus.  In the military engagement domain the three test points were located on the vertical line that bisected the stimulus: P1 was located near the enemy tanks, P3 was located with all friendly units between it and the enemy tanks and P2 was located near the center of the image as follows. In stimuli (j) and (k) the point lay between all forces, in stimulus (i), it lay behind the friendly tanks, and in stimulus (l) , it lay behind the lone turret but in front of the row turrets.  P3 was the expected \textit{sweetspot} in the military engagement domain but the rating of P2 should differ with (i) receiving the highest score and (k) the lowest score.

@@

%Task 1: The participant draws a polygon denoting the region
%Analysis of results:
%(1) Do participants agree/understand-the-task? (validation of approach) + Should anyone be excluded?
%Within the data for each trial,
%-- For each participant, generate the intersection and union polygon of all the other participants
%---- Generate N random points in the area of the full stimulus
%---- For each of these N points check whether the participant's polygon and the [intersection/union] polygon both include it (agree++) or if one includes it and the other doesn't (disagree++)
%---- Then we calculate a \textit{Cohen kappa} score as a measure of agreement between the participant and eveyone else. Note we need to calculate the chance of random agreement but we can do this as a function over the relative size of the participant's polygon in the total area of the stimulus and the relative size of the intersection/union polygon
%(see http://en.wikipedia.org/wiki/Cohen%27s_kappa )
%This process will result in for each trial a list of kappa scores for each participant indicating the extent to which they agree with everyone else. We are hoping for a high kappa score
%(2) Does context matter?
%I understand that all the rooms stimuli have the same extent.
%So one way of evaluating whether context matters is to use the kapp score between the intersection/union polygon generated using all the response (less the excluded partitipants) for one trial and the equivalent polygon for another trial.
%We are hoping for a low kappa score

%\textit{Cohen's kappa} measures the agreement between two annotators who each classify a number of items into two or more mutually exclusive classes as is defined as follows:
%\begin{equation*}
%\kappa = \frac{P(a)-P(ca)}{1-P(ca)}
%\end{equation*}
%where $P(a)$ is the observed relative agreement between the annotators, and $P(ca)$ is the probability of a chance agreement between these to annotators.

@@

%The type 2 trials the same visual stimulus and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on %the visual stimulus (using a red dot) and the subject was asked to rank on a five point \textit{Likert scale} their judgement of how well the location matched %the described spatial region. For each stimulus domain (classroom, map, military engagement) three points (P1, P2, and P3) were pre-selected.

Table \ref{tab:point-likert-scores} lists the average Likert scores for the different points in each context. In all contexts, the expected \textit{sweetspot} received the maximum average Likert rating that was statistically significant using one-tailed two-sample t-tests $(p<.05)$.  To control for left--right bias, we compared the ratings of \textit{sweetspots} in the classroom stimuli (c), (e), and (f) with their flipped variants.  There was no statistical difference between the stimuli and their flipped variants.  These Likert ratings on individual stimuli support the claim that people are able to agree on the locations of CDSRs with changing context.

%There were two of these t-tests carried out for each stimulus, each one tested whether the \textit{sweetspot} ranking was statistically higher than one of the other points. Table \ref{tab:point-likert-scores} also lists the results of these t-tests for each stimulus. In all cases, the results indicate that the null hypothesis, $H_0$, should be rejected and that the alternative hypothesis, namely that the \textit{sweetspot} was rated significantly higher than the other point, could be accepted with $\alpha=0.05$.

%As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the \textit{sweetspots} rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the \textit{sweetspot} for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the \textit{sweetspots} occurred we ran two-tailed two-sample t-tests between the \textit{sweetspots} of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the \textit{sweetspot} for the non-flipped stimuli and the rating of the \textit{sweetspot} for the flipped stimuli using a confidence level of $95\%$. In other words, the \textit{sweetspot} flipped from P1 to P3 systematically with the horizontal flipping of the stimuli. %lending support for question 2 ...

@@

Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the military domain between the stimuli (i) and (j) and the stimuli (k) and (l). In stimulus (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimulus (j) the P2 point is in \textit{no-man's land}\footnote{We use the term no-man's land to describe the unoccupied and contested area between the opposing forces.}. Given this change in context one would expect a higher ranking for the P2 point in context (i) than in context (j). This is confirmed by the results in Table \ref{tab:point-likert-scores} and the higher rating is statistically significant $(p<.05)$. Stimuli (k) and (l) present an analagous context with P2 being protected by an extra turret in stimulus (l) but in no-man's land in stimulus (k). Again, the average rating of P2 for stimulus (l) is higher than that of (k), although this difference is not statistically significant. Thus, it is unclear the extent to which participants were simulating the outcome of the battle. Notice, that the rating of the \textit{sweetspot} for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different \textit{sweetspots} across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.

@@

Taken together these results indicate that: (1) for all stimuli there was a location that was considered to be inside the region described by the linguistic term and that other locations were considered to be outside of this region; (2) within each domain the particular location that was considered to be the \textit{sweetspot} was determined by the particular context depicted in the visual stimulus (i.e., changes in the position and orientation of objects with functional significance effected the location of the region); and (3) the impact of the changes in the depicted context was consistent across similar contexts, as shown by the fact that the \textit{sweetspot} flipped from P1 to P3 when the context was flipped.

%-----------------
%
%Task 2: The participant selected a point denoting the \textit{sweetspot} of the region
%Analysis of results:
%(1) Do participants agree/understand-the-task? (validation of approach) + Should anyone be excluded?
%Compare the variance across the subjects with the variance across a number of set of randomly generate points, where set size equals the number of participants, using the F distribution (http://www.ltcconline.net/greenl/courses/201/regression/comparingVariances.htm) where we are checking if the variance of the random points are greater than that of the participants.
%We would hope that the variance of the subjects responses is lower than that of randomly generated points.
%After the initial comparison with the random point sets we may exclude participants based on extreme variance.
% 
%(2) Does context matter?
%Do the clusters of participants responses move?
%- for each experimental stimulus compute the mean x and y location for the responses for that trial
%- check whether the variance between the means of different stimuli responses is greater than the variance within each stimulus responses.

%-----------------
%
%
%Task 3: The participant grades a point with respect to membership of the region on a \textit{Likert scale}
%I understand this experiment to be useful because (a) it asks the participants to evaluate (rather than generate cf task 1 and 2) (b) hopefully we can use it to reinforce our findings in task 1 and task 2
%I think we need to be careful that the points we present to people for evaluation are reasonably well distributed so that we have a good chance of getting a variation across the responses
%Assuming that there is a variation across the Likert scores for a particular stimulus then check if their is a correlation between the scores and:
%(a) inclusion in the intersection/union polygons from task 1 for the same stimulus
%(b) distance from the mean sweet spot for that stimulus from task 2
%
%-----------------

@@

%Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to qualiative spatial reasoning (QSR) work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.
%
%However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all the way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.
%
%The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.
